\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-24 OaklandSubmission/intro.tex

\item To address this issue of efficient representation, recently Demmler et al. \cite{aby} gave a cryptographic protocol for \mpc where the functionality can be expressed as a circuit with a mix of both arithmetic and boolean parts.
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, in their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate
inter-conversion gates.
This requires the programmer to be aware of
trade-offs between arithmetic and boolean cryptographic
schemes as well as the complex inter-conversion costs between arithmetic and boolean, and manually split the functionality into such parts accordingly.  
In short, as is also mentioned by Demmler et al., the current system  is not suitable
to be used by \divya{non-cryptography expert developers. }

@@

In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
computation. We provide the first compiler where the developer writes a high-level program and the compiler automatically generates an efficient \mpc protocol that uses a
mix of Arithmetic and Boolean compute. 
It is compatible with any implementation of \mpc that allows a mix of arithmetic and boolean computations. 
We focus on semi-honest secure two-party computation and use ABY \cite{aby} as the suitable cryptographic back-end.
We provide a formal type system and operational semantics for our language and prove correctness and security of our compiler.
We evaluate our system on wide range of benchmarks \cite{shafindss,wu,minionn,valeriaMatrix} computing linear classifier, decision trees, deep neural networks, and matrix factorization. Our evaluations show that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). \divya{Moreover, unlike previous systems, our system can scale to arbitrarily large computations using {\em pipelining} (see below). What do we say about Yao pipelining?}
Hence, we show that our framework achieves all four properties of generality, performance, programmer productivity and scalability.

>>>>

\item To address this issue of efficient representation, recently Demmler et al. \cite{aby} gave a cryptographic protocol for \mpc where the functionality can be expressed as a circuit with a mix of both arithmetic and boolean parts.
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, in their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate
inter-conversion gates.
This requires the programmer to be aware of
trade-offs between arithmetic and boolean cryptographic
schemes as well as the complex inter-conversion costs between arithmetic and boolean, and manually split the functionality into such parts accordingly.  
In short, as is also mentioned by Demmler et al., the current system  is not suitable
to be used by non-specialist programmers without security expertise.

@@

In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
computation. We provide the first compiler where the developer writes a high-level program and the compiler automatically generates an efficient \mpc protocol that uses a
mix of arithmetic and boolean circuits. 
It is compatible with any implementation of \mpc that allows a mix of arithmetic and boolean circuits. 
We focus on semi-honest secure two-party computation and use ABY \cite{aby} as the suitable cryptographic back-end.
We provide a formal type system and operational semantics for our language and prove correctness and security of our compiler.
We evaluate our system on wide range of benchmarks for secure prediction \cite{shafindss,wu,barni,secureml,minionn,bonsai} using linear classifier, decision trees and deep neural networks, matrix factorization \cite{valeriaMatrix} and training of deep neural network \cite{secureml}. Our evaluations show that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). \TODO{Add some text to increase enthusiasm about results.} Moreover, unlike previous systems such as \cite{wysteria,aby}, our system can scale to arbitrarily large computations using {\em secure code partitioning} (see below). \divya{I think we can skip Yao pipelining here, right?}
Hence, we show that our framework achieves all four properties of programmability, generality, performance, and scalability.
